Trait plasticity and covariance along a continuous soil moisture gradient

### 2020-03-05 FVT Manuscript/manuscript.Rmd
minor changes

author: 
  - name          : "J. Grey Monroe"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "262 Robbins Hall, UC Davis, One Shields Ave, Davis CA 95616"
    email         : "greymonroe@gmail.com"
  - name          : "Haoran Cai"
    affiliation   : "2"
  - name          : "David L. Des Marais"
    affiliation   : "2,3"
affiliation:
  - id            : "1"
    institution   : "Department of Plant Sciences, University of California at Davis, Davis, USA"
  - id            : "2"
    institution   : "Department of Civil and Environmental Engineering, Massachusetts Institute of Technology, Cambridge, MA, USA"
  - id            : "3"
    institution   : "The Arnold Arboretum of Harvard University. Boston, MA, USA"

@@

# Acknowledgements
We thank Chase Mason and Eric Goolsby for insightful conversations about function-valued trait approaches. This work was supported by an Eco-Evo-Devo Network training grant to JGM.

@@

(ref:maps) Distributions of (a) _B. distachyon_ and (b) _B. sylvaticum_ reported on GBIF as of 2019.18.08. Examples of (c) _B. distachyon_ Carly Slawson (CC BY 4.0, https://www.inaturalist.org/photos/42532397) and (d) _B. sylvaticum_ Grzegorz Grzejszczak (CC BY-NC 4.0, https://www.inaturalist.org/photos/3608899).

>>>>

author: 
  - name          : "J. Grey Monroe"
    affiliation   : "1,4"
    corresponding : yes    # Define only one corresponding author
    address       : "Current address: 1 Max Planck Ring, 72076 Tubingen, DE"
    email         : "greymonroe@gmail.com"
  - name          : "Haoran Cai"
    affiliation   : "2"
  - name          : "David L. Des Marais"
    affiliation   : "2,3"
affiliation:
  - id            : "1"
    institution   : "Department of Plant Sciences, University of California at Davis, Davis, USA"
  - id            : "2"
    institution   : "Department of Civil and Environmental Engineering, Massachusetts Institute of Technology, Cambridge, MA, USA"
  - id            : "3"
    institution   : "The Arnold Arboretum of Harvard University. Boston, MA, USA"
  - id            : "4"
    institution   : "Max Planck Institute for Developmental Biology, Tubingen, DE"

@@

# Acknowledgements
We thank Chase Mason and Eric Goolsby for insightful conversations about function-valued trait approaches. This work was supported by an Eco-Evo-Devo Network training grant, USDA-NIFA Award 2014-38420-21801, and Max Planck Society support for JGM.

@@

(ref:maps) Distributions of (a) _B. distachyon_ and (b) _B. sylvaticum_ reported on GBIF as of 2019.18.08. Examples of (c) _B. distachyon_ Carly Slawson (CC BY 4.0, https://www.inaturalist.org/photos/42532397) and (d) _B. sylvaticum_ Grzegorz Grzejszczak (CC BY-NC 4.0, https://www.inaturalist.org/photos/36088991) (GBIF.org (26 February 2020) GBIF Occurrence Download https://doi.org/10.15468/dl.rau5v9).
